\ttitle

### 2013-05-13 Chapters/Chapter2.tex
Add HTML version of PDF to repo.
Execute `pdf2htmlEX main.pdf` to regenerate it.
Write on SVM segmentation
Write about statistical models

>>>>

\section{Statistical framework}
Many applications require the detection of time points at which underlying properties of a system change.
This problem thus has received a lot of attention in the fields of data mining, etc... *** list and refs ***.

Some methods, such as the CUSUM (cumulative sum) \cite{basseville1993detection} and GLR (generalized likelihood ratio) \cite{gustafsson1996marginalized, gustafsson2000adaptive} formulate this problem in the statistical framework in the following sense.
A time series is represented by an underlying probability distribution generating the data.
The PDFs (probability distribution function) of two consecutive segments around a target point are compared.
If they differ significantly, the target point is considered as a change point \cite{kawahara2009change}.

%----------------------------------------------------------------------------------------
\section{Change-detection by Dimensionality Reduction / Covariance structure}

%----------------------------------------------------------------------------------------
\input{./Chapters/Chapter2/density_ratio}

%----------------------------------------------------------------------------------------
\input{./Chapters/Chapter2/svm}

%----------------------------------------------------------------------------------------
\section{Change-detection by Cumulative Sum}
